A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-24 text/manuscript.Rmd
minor edit to main doc

All code for producing the analyses and figures herein are included in this
fully reproducible manuscript in R markdown format. R markdown files and all
other models are available from [our
repositories](https://github.com/dennishazelett/TTmanu) in the following
locations on the distributed version control site GitHub.

>>>>

All code for producing the analyses and figures herein are included in this
fully reproducible manuscript in R markdown format. R markdown files and all
other models are available from [our
repositories](https://github.com/dennishazelett/TTmanu) on the distributed
version control site, GitHub.
